When the Pen Becomes a Sword: Retired US Military Officers and Op-Ed Use in Contemporary America

### 2020-08-13 code/Submissionv2.Rmd
commit

```{r second level analysis, include = FALSE}
# Present Results of Result and Justification
secondlayer_obs <-adjdataset %>% arrange(PubYr) %>% 
  filter(MilPSoc==1 | Dom_P==1 | Fig_Nme==1 )  %>% 
  filter(Author != "UNK") %>% filter(Author != "Murtha, John") %>% 
  select (Author, Title, Source, PubYr, Ques_Prof, Justification) %>% 
  view()

#Now Prep the data that I need to analyze polarization levels.  I will try first by 
# eliminating the NA values but I will do this by indexing the first 334 rows of the 
# data, which corresponds to the number of observations that I have.  I do this by #creating a new data set called slimdata

@@

predictiondata <- tibble(House_polarization_level=seq(min(slimdata$House_distance_dim1), max(slimdata$House_distance_dim1), by=.01), Credibility = mean(slimdata$Inst_Cred_Gallup)) %>%
crossing(Ques_Prof = c(0,1), MilPSoc = c(0,1), Dom_P = c(0,1), Fig_Nme = c(0,1))

@@

predictions <- augment(logmodel, newdata=predictiondata) %>% 
  mutate(
    .prob=plogis(.fitted),
    conf.low = plogis(.fitted -(qnorm(.975) * .se.fit)),
    conf.high = plogis(.fitted + (qnorm(.975) * .se.fit)),
    pred_final_rec = case_when(
      .prob >= .5 ~ "Likely Violation of Professionalism",
      .prob < .5 ~ "Violation of Professionalism not likely"
    )
  ) 
predictions %>% arrange(.prob, .fitted, Report, Night, desc(.fitted)) %>% 
  view()

>>>>

```{r second level analysis, include = FALSE}
# Present Results of Result and Justification
secondlayer_obs <-adjdataset %>% arrange(PubYr) %>% 
  filter(MilPSoc==1 | Dom_P==1 | Fig_Nme==1 )  %>% 
  filter(Author != "UNK") %>% filter(Author != "Murtha, John") %>% 
  select (Author, Title, Source, PubYr, Ques_Prof, Justification) %>% 
  view()
```

```{r polarization logit analysis, include=FALSE}

#Now I Prep the data that I need to analyze polarization levels.  I will try first by 
# eliminating the NA values but I will do this by indexing the first 334 rows of the 
# data, which corresponds to the number of observations that I have.  I do this by #creating a new data set called slimdata.

# Note: this is sloppy.  There has to be a better way to get rid of NA values.

@@

predictiondata <- tibble(House_distance_dim1=seq(min(slimdata$House_distance_dim1), max(slimdata$House_distance_dim1), by=.01), Inst_Cred_Gallup = mean(slimdata$Inst_Cred_Gallup)) %>%
crossing(Ques_Prof = c(0,1), MilPSoc = c(0,1), Dom_P = c(0,1), Fig_Nme = c(0,1))

@@

predictions <- augment(logmodel, newdata=predictiondata) %>% 
  mutate(
    .prob=plogis(.fitted),
    conf.low = plogis(.fitted -(qnorm(.975) * .se.fit)),
    conf.high = plogis(.fitted + (qnorm(.975) * .se.fit)),
    pred_final_rec = case_when(
      .prob >= .5 ~ "Likely Violation of Professionalism",
      .prob < .5 ~ "Violation of Professionalism not likely"
    )
  ) 
predictions %>% arrange(.prob, .fitted, MilPSoc, Dom_P, Fig_Nme, desc(.fitted)) %>% 
  view()

# stopping point here.  now let's try some graphs
# notice that the predictions are not in (0, 1)
ggplot(predictions) +
  aes(x = .fitted) +
  geom_histogram()

# if we wanted predictions on the probability scale,
#   we predict on the log scale,
#   then apply inverse-logit (logistic CDF)
# use plogis(): cumulative probability of the logistic distribution

# demonstration: scatter log odds (x) and predicted probability (y)
# with 95% CIs
# (CIs don't look smooth in this example because .se.fit depends on X data)
predictions %>%
  ggplot() +
  aes(x = .fitted, y = .prob) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high)) +
  geom_smooth() 
```
```
